### 2014-02-27 paper/formal.tex
Add missing label.

\begin{theorem}[Concurrent specification language is TSNI]
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}

>>>>

\begin{theorem}[Concurrent specification language is TSNI].
  \label{thm:rr-tsni}
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}
